Detecci\'on de malas hierbas a trav\'es\\ de t\'ecnicas de redes neuronales convolucionales y visi\'on artificial

### 2017-05-04 PaperBCJ.tex
Subsecciones agregadas
Fist part of the State of the Art

% As a general rule, do not put math, special symbols or citations
% in the abstract
\begin{abstract}
The abstract goes here.
\end{abstract}

@@

\section{Introduction}
% no \IEEEPARstart
This demo file is intended to serve as a ``starter file''
for IEEE conference papers produced under \LaTeX\ using
IEEEtran.cls version 1.8b and later.
% You must have at least 2 lines in the paragraph with the drop letter
% (should never be an issue)
I wish you the best of success.

@@

@@

\bibitem{IEEEhowto:kopka}
H.~Kopka and P.~W. Daly, \emph{A Guide to \LaTeX}, 3rd~ed.\hskip 1em plus
  0.5em minus 0.4em\relax Harlow, England: Addison-Wesley, 1999.

>>>>

% As a general rule, do not put math, special symbols or citations
% in the abstract
\begin{abstract}
Today the computation stays i 
\end{abstract}

@@

\section{Introduction}
% no \IEEEPARstart

% You must have at least 2 lines in the paragraph with the drop letter
% (should never be an issue)
I wish you the best of success.

@@

\section{State of Art}
Along the last centuries there had been developed  huge progress in the science and technology, significant milestones such as Communications, Computer Numerical Control and the miniaturization of components has permitted to the social and industrial sectors to benefit in order to reach their objectives.

The globalization in the world also allow to countries like Ecuador(which isn’t larger producer of technology) to receive products and technological knowledge to satisfy requirements o propose   solutions for problems of the country still unresolved.

The transformation of the industry is a example of the evolution of the science, the Manufacturing , the Food and Drink,Information Industries, etc. are signs of this industrial revolution. However there are fields still unexplored  in Ecuador like the agroindustry. Agriculture in Ecuador has changed a bit since the epoch of the Incas, it isn’t so bad mainly due there are good agriculture knowledge like terraces but the faulty exploitation of technological resources make impossible to the country to exploit its true potential like agricultural producer.

Today the agriculture has many challenges for the Precision Agriculture such as the Weed and Crop segmentation \cite{Brivot:Marchant} ,

\section{Implementation of the Algorithm}
%Codigo para la Implementacion del Algoritmo

\section{Test}
%Codigo para la Implementacion del Algoritmo

@@

\bibitem{Brivot:Marchant}
R.~Brivot and J.~A. Marchant, \emph{Segmentation of plants and weeds for a precision crop protection robot using infrared images}\hskip 1em plus
  0.5em minus 0.4em\relax Harlow, England: IEE Proc-Vis Image Signal Process, 1996.

\bibitem{IEEEhowto:yo}
Youtube, \emph{Gmail \LaTeX}, 3rd~ed.\hskip 1em plus
  0.5em minus 0.4em\relax Harlow, England: Addison-Wesley, 1999.
